Concurrent Programming with CXL

### 2020-06-24 book/paper.tex
Made a pass over barrier synchronization

Barrier synchronization is a problem that comes up in high-performance
parallel computing, used, among others, for scalable simulation.
Barrier synchronization is almost the opposite of critical sections:
the intention is to get a group of processes to run some code at the
same time.
More precisely, the processes run in rounds.  At the end of each round
there is a so-called \emph{barrier} where processes wait until all
processes have completed the round.
For example, in an iterative matrix algorithm, the matrix may be
cut up into fragments.  During a round, one process runs for each
fragment concurrently.  The next round is not allowed to start
until all processes have completed operations on their fragment.

@@

\section*{Exercises}
\begin{problems}
\item See if you can implement barrier synchronization for $N$ processes
with just three semaphores.  Busy waiting is not allowed.  How about just two?
\item Implement barrier synchronization with Mesa condition variables.
\end{problems}

>>>>

Barrier synchronization is a problem that comes up in high-performance
parallel computing, used, among others, for scalable simulation.
A barrier is almost the opposite of a critical section:
the intention is to get a group of processes to run some code at the
same time, instead of having them execute it one at a time.
More precisely, with barrier synchronization the processes execute in rounds.
Between each round there is a so-called \emph{barrier} where processes wait
until all processes have completed the round and before they start the
next one.
For example, in an iterative matrix algorithm, the matrix may be
cut up into fragments.  During a round, the processes run concurrently
one for each fragment.  The next round is not allowed to start
until all processes have completed processing their fragment.

@@

\section*{Exercises}
\begin{problems}
\item See if you can implement barrier synchronization for $N$ processes
with just three semaphores.  Busy waiting is not allowed.  How about just two?
(As always, the Little Book of Semaphores~\cite{Downey09} is a good resource
for solving semaphore problems.  Look for the double turnstile solution.)
\item Implement barrier synchronization with Mesa condition variables.
(You may want to use a double turnstile approach here as well.)
\end{problems}
